Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-12 prop.tex
prop.tex \section{Introduction} Updating...

We will begin by reviewing existing work that recasts classical probability
spaces in a resource-aware setting and move to aim at recasting quantum
probability and hence quantum measurement to a corresponding resource-aware
setting. In particular, we develop a measurement framework based on
quantum interval-valued probability measures. Surprisingly, we found
a quantum IVPM which can not be induced by a state while Shapley proved
a classical convex IVPM can always be induced by a classical ``state''~\cite{Shapley1971,Grabisch2016},
and Gleason proved a infinitely-specified quantum probabilities measure
can always be induced by a quantum state~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Nevertheless, a quantum IVPM could still correspond to many states
while we break it into pieces. Our examples also suggest that a quantum
IVPM could be more and more likely induced by a state while the intervals
become sharper, i.e., the measurement resources increase.

Since Gleason's theorem supports the idea of von Neumann to formulate
quantum states as points in a projective Hilbert space, a point in
a projective Hilbert space might not be the adequate imprecise quantum
``state.'' Instead, a quantum state might be more like an interactive
system suggested by Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
which would be different for different interactor. Furthermore, the
fundamental theorems of quantum mechanics followed up by Gleason's
theorem , such as Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
might need to be reassessed the validity with imprecise measurement.
Our research then might provide a new insight to the old debate whether
finite precision measurement would nullify the Kochen-Specker theorem
or not, by Meyer, Mermin, and others~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004}.

>>>>

We will begin by reviewing existing work that recasts classical probability
spaces in a resource-aware setting and move to aim at recasting quantum
probability and hence quantum measurement to a corresponding resource-aware
setting. In particular, we develop a measurement framework based on
quantum IVPM. Surprisingly, we found a quantum IVPM which can not
be induced by a state, while Shapley proved a classical convex IVPM
can always be induced by a classical ``state''~\cite{Shapley1971,Grabisch2016},
and Gleason proved a infinitely-specified quantum probabilities measure
can always be induced by a quantum state~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Nevertheless, a quantum IVPM could still correspond to many possible
states if we break it into pieces. Our examples also suggest that
a quantum IVPM could be more and more likely induced by a state while
the intervals become sharper, i.e., the measurement resources increase.

Since Gleason's theorem supports the idea of von Neumann to formulate
quantum states as points in a projective Hilbert space, a point in
a projective Hilbert space might not be the adequate imprecise quantum
``state.'' Instead, a quantum state might be more like an interactive
system suggested by Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
which would be different for different interactor. Furthermore, the
validity the fundamental theorems of quantum mechanics followed up
by Gleason's theorem, such as Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
might need to be reassessed based on our imprecise measurement. Our
research then might provide a new insight to the old debate among
Meyer, Mermin, and others about whether finite precision measurement
would nullify the Kochen-Specker theorem or not~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004}.
